Innovations Report: Procedural Fur System

### 2018-03-18 docs/paper.tex
more on docs

\section{Introduction} \label{sec:introduction}
Introduction Text.
\subsection{Related work} \label{sec:related}
nvidia hairworks

@@

Overall I am pleased with the visual quality and interactivity of my system, but I believe further work is necessary in order to maximise it's performance and usability.

>>>>

\section{Introduction} \label{sec:introduction}
Introduction Text.
\subsection{Related work} \label{sec:related}

nvidia hairworks

@@

Overall I am pleased with the visual quality and interactivity of my system; currently it provides the basic functionality required to visualise simple hair and fur content, whether it be for a VFX or real-time usage scenario. However, I believe further work is necessary in order to maximise it's performance and usability within a broader production pipeline.
